---
title: "Prediction Model"
author: "Dengjiahao"
output: html_document
---
This easy is going to build a machine learning a lgorithm to predict activity quality    from activity monitors.    

The training data for this project are available [here](https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv)  
The test data are available [here](https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv)   

So, first let's read the data.   
```{r,cache=TRUE}
data<-read.csv("pml-training.csv")
library(caret)
library(kernlab)
inTrain<-createDataPartition(y=data$classe,p=0.7,list=FALSE)
training<-data[inTrain,]
testing<-data[-inTrain,]
```   



Then, let's build the random forests model to predict.   
Since there are some variables that contains NA values, I choose some variables as predictors. They do not contain so many NA values.   

```{r,cache=TRUE}
model<-train(classe~new_window+num_window+roll_belt+pitch_belt+yaw_belt+total_accel_belt+gyros_belt_x+gyros_belt_y+gyros_belt_z+accel_belt_x+accel_belt_y+accel_belt_z+magnet_belt_x+magnet_belt_y+magnet_belt_z+roll_arm+pitch_arm+yaw_arm+total_accel_arm+gyros_arm_x+gyros_arm_y+gyros_arm_z+accel_arm_x+accel_arm_y+accel_arm_z+magnet_arm_x+magnet_arm_y+magnet_arm_z+roll_dumbbell+pitch_dumbbell+yaw_dumbbell,data=training,method="rf")
```     

Then, we can exam the prediction model using the function accuracy.    
```{r,cache=TRUE}
accuracy<-function(values,prediction){sum(prediction == values)/length(values)}
prediction<-predict(model,testing)
accuracy(testing$classe,prediction)
```   

So, we can tell that the accuracy is very high.    
let's generate the answer of the test file.  

```{r,cache=TRUE}
testing2<-read.csv("pml-testing.csv")
answers<-predict(model,testing2)
answers
```   

Finally, let's generate the files to submit for the submission part.  
```{r,cache=TRUE}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
pml_write_files(answers)
```   

